---
title: "nicertables package vignette"
author: "Jennifer lay"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{nicertables package vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## 1. How to use the make_cor_tables() function

This function can be used with any numerical raw data.

First, open the raw data file and stick it in a dataframe. There is a raw data file included with this package, called "raw_data_for_correlation_calculation.csv". Here's how to access it:

```{r, echo=FALSE, results='asis'}
raw_data_for_correlation_function <- as.data.frame(readr::read_csv(
            system.file("extdata", "raw_data_for_correlation_calculation.csv", package = "nicertables")))
```

You can then simply stick the dataframe into the make_cor_tables() function. The function will then write a nice correlation table to file (a .csv file is what it makes now), and a corresponding correlation p value table (another .csv file).

Let's use the function with just the raw data file, and the defaults for all other parameters

```{r, echo=FALSE, results='asis'}
correlation_output <- nicertables::make_corr_tables(input_data = raw_data_for_correlation_function)

```

We now how two output files, "corrs_mat_data.csv" and "corrs_mat_data.csv", located in your home directory. This is the default behaviour (we'll see how to modify it below).

The function also returns an object of type psych. It holds a bunch of information about your correlation table. 

For example, to access the correlation table:

```{r, echo=FALSE, results='asis'}
correlation_output$r

```

And to access the correlation p values:

```{r, echo=FALSE, results='asis'}
correlation_output$p

```

Let's try the other function parameters:
- Use the path_name parameter to specify where you want your output files to go (default is your home directory, "~/")
- Use the data_name parameter to specify a name for your output files (default is "data")

Here's an example where we change data_name:

```{r}
nicertables::make_corr_tables(input_data = raw_data_for_correlation_function, path_name = "~/", data_name = "my_name")

```

We now how two output files, "corrs_mat_my_name.csv" and "corrs_mat_my_name.csv", located in your home directory.

## 2. How to use the make_reg_tables() function

Coming soon ...

